Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
Work on paper2.tex

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network.
We also consider a deterministic state-machine $M$ whose set of commands is $C$ and equipped with a dependency relation $R \subseteq C\times C$ such that for any command $c$, $\left( c,c \right)\notin R$; for any commands $c_1$ and $c_2$, if $\left( c_1,c_2 \right)\in R$ then $\left( c_2,c_1 \right)\in R$; if $\left( c_1,c_2 \right)\in R$ and $\aseq{s_1,c_1,s_2,c_2,\cdots,s_n}$

@@

A map-agreement algorithm exposes

\printbibliography%

>>>>

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network.
We also consider a deterministic state-machine $M$ whose set of commands is $C$ and equipped with a dependency relation $R \subseteq C\times C$ such that for any command $c$, $\left( c,c \right)\notin R$; for any commands $c_1$ and $c_2$, if $\left( c_1,c_2 \right)\in R$ then $\left( c_2,c_1 \right)\in R$; if $\left( c_a,c_b \right)\in R$ then $\aseq{s_1,c_1,\cdots,s_i,c_a,s_{i+1},c_b,\cdots,s_n}$ is an execution of the state-machine $M$ if and only if
$\aseq{s_1,c_1,\cdots,s_i,c_b,s_{i+1},c_a,\cdots,s_n}$.

@@

A map-agreement algorithm exposes the input action $propose\left( c, deps \right)$

%\printbibliography%
\bibliography{managed}{}
\bibliographystyle{plain}
